---
title: "Executing Reward"
date: "`r Sys.Date()`"
always_allow_html: yes
output:
  pdf_document:
    number_sections: yes
    toc: yes
    template: null
  html_document:
    number_sections: yes
    toc: yes
  rmarkdown::html_vignette: default
vignette: |
  %\VignetteIndexEntry{Executing Reward}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css echo=FALSE}
h1  {
  margin-top: 60px;
}
```
# Introduction
REWARD is designed to be a rapid platform for producing population level effect estimates from observational healthcare data.
This package forms the execution proportion of REWARD - the minimum amount of code required to generate results.

Note: further analysis (unblinding) of results requires a more principled approach than is provided in this vignette

# Installation and configuration of execution environment

We recommend creating a new RStudio project and using `renv` to manage packages related to REWARD.

```{r eval=FALSE}
# In a new rstudio environment
install.packages("renv")
renv::init()
```
The next step is to install the latest version of the `RewardExecutionPackage`.
This can be achieved as follows (requires `remotes` R package).

```{r eval=FALSE}
# In a new rstudio environment
install.packages("remotes")
remotes::install_github("ohdsi/RewardExecutionPackage")
```
Providing your environment is configured correctly, the package should be installed correctly.

# Creating a CDM configuration YAML file
To execute the REWARD components we must first create a configuration file that determines the usage of a CDM.
This details the relevant tables, database schemas and other parameters required to execute a study.
The simplest way to do this is to use the utility function provided in the package as follows:

```{r eval=FALSE}
createCdmConfiguration("myCdmConfig.yml", useKeyring = TRUE)
```
This will create the file `myCdmConfig.yml` and load up an editor that will require you to alter the configuration specific to your cdm.

## Data source information

This should be information that is unique to your CDM.
The `sourceId` won't be relevant unless it is registed in the central reward database.
However, the database and name should be the cdm on your system.
```{yml}
sourceId: 0
database: MyCdmDatabaseName
name: MyCdmFriendlyName
```
## File storage

```{yaml}
exportPath: "export"
referencePath: "reference_files"
```
The file storage locations are crucial, the path to `export` should be a location on disk that is at least 25GB in size
as results from the REWARD analysis can be large.

The reference files path is just a location where the cohort definitions for reward can be stored.
These should be provided from the central reward database.

## Setting Connection Details
Crucially, reward needs to be able to connect to your CDM.
These settings should conform to a `DatabaseConnector connectionDetails` object.
However, reward does not require a password to be stored in plaintext in this configuration (though, this can optionally be done
if you have lower security requirements).
```{yaml}
connectionDetails:
  dbms: "postgresql"
  server: "localhost/reward"
  port: 5432
  # If username is unset it will be the system username
  # Alternatively, set environment variable REWARD_CDM_USER
  user: "postgres"

# use keyring package for storing database credentials
useSecurePassword: True
keyringService: "reward_cdm"

# Use DatabaseConnector bulk upload, where possible
# See DatabaseConnector documentation for more information
bulkUpload: True
```
Because the `useSecurePassword` parameter is set to true, the database password you use for your cdm will be stored securely for reuse
using the r `keyring` package.
You should be prompted for this password when you press save.
For more details on how this works, consult the keyring documentation [here](https://r-lib.github.io/keyring/index.html).
If you intend to execute this packge on multiple cdms that have the same user credentials, this information does not
need to be re-entered when you

## Schemas and tables
The following settings are likely specific to your CDM and need to be configured.
We strongly suggest you have an isolated `reward` database schema for reward that can be written to, separate from your CDM.
This single schema can contain cohort results as well as references.
The location of your cdm and vocabulary may be the same.
```{yaml}

# Where cohort results are stored
resultSchema: "reward"
# Where reference files are imported
referenceSchema: "reward"
# OMOP Common Data Model Schema
cdmSchema: "cdmv5"
# schema that contains OMOP vocabulary tables
vocabularySchema: "cdmv5"
# Optional: schema for storing custom drug eras
drugEraSchema: "reward"
```
These are the tables used by reward.
These only need to be changed if they conflict with other tables in your schema (e.g. if you are executing reward on multiple CDMS on the same database).
```{yaml}
# Tables to be created and used by REWARD
tables:
  outcomeCohort: "outcome_cohort"
  cohort: "exposure_cohort"
  sccResult: "scc_result"
  # Reference table definitions
  cohortDefinition: "cohort_definition"
  outcomeCohortDefinition: "outcome_cohort_definition"
  conceptSetDefinition: "concept_set_definition"
  atlasOutcomeReference: "atlas_outcome_reference"
  atlasOutcomeConcept: "atlas_outcome_concept"
  atlasExposureReference: "atlas_exposure_reference"
  atlasExposureConcept: "atlas_exposure_concept"
  customExposure: "custom_exposure"
  customExposureConcept: "custom_exposure_concept"
  analysisSetting: "analysis_setting"
```
## Testing the configuration
By default, the information you use will be tested.
This includes connecting to the database and ensuring that all the relevant schemas exist and the user has read/write permissions to the relevant database schemas.
If, at any point, you manually edit the yaml configuration remember to call `validateCdmConfigFile` to test if the parameters are valid.


# Executing the REWARD study
The simplest way to execute REWARD is to use an Rstudio session with the following code.
```{r eval = FALSE}
#TODO

```

Alternatively, you can use the execute function from inside an r session

```{r eval = FALSE}
execute(cdmConfigPath, referenceZipFile, deleteExistingCohorts = deleteExistingCohorts)
```

# Uploading results
First your CDM must be registered within the REWARD database.

The results CSV files can then be shared with the OhdsiSharing package.
```{r}
# TODO
```
Once compiled, the post processing, analysis and viewing of results can be completed.
